Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-10-31 index.qmd
add date and more motivation

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
subtitle: "Presentation on Social Mobility - Wicksell 30/10/2023"
author: "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://interludeone.com)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---

@@

@@

::: {.column width="50%"}
![](assets/robot.png){fig-align="center" width=60%}
:::

@@

@@

timeline %>%
    filter(!is.na(start_year)) %>%
  arrange(start_year) %>%
  mutate(end_year_imputed = case_when(
    is.na(end_year) ~ lead(start_year),
    is.na(lead(start_year)) ~ start_year,
    TRUE ~ end_year
  )) %>%
  mutate(
    event = fct_reorder(event, start_year, .desc = TRUE)
  ) %>%
  # pivot_longer(c(start_year, end_year_imputed)) %>%
  # ggplot(aes(value, english_occupation, colour = name)) +
  ggplot(aes(xmin = start_year, xmax = end_year_imputed, y = event)) +
  geom_linerange(colour = "gray50", size = 2) +
  geom_point(aes(x = end_year_imputed), colour = "#be5d2b", size = 4) +
  geom_point(aes(x = start_year), colour = "#2B8CBE", size = 4) +
  labs(
    title = "Karl Lund's life course",
    subtitle = "Showing <span style = 'color:#2B8CBE;'>start dates</span> and <span style = 'color:#be5d2b;'>end dates</span> for his various roles and life events",
    x = NULL,
    y = NULL
  ) +
  theme(
    legend.position = "none",
    plot.subtitle = element_markdown(),
    plot.title.position = "plot",
    text = element_text(family = "ibm", size = 28)
  )

@@

@@

@@

watchmaker_table
```

@@

occupation_table

@@

>>>>

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
subtitle: "Presentation at SDU for the group working on Human Capital in the Nordics"
date: today
author: "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://interludeone.com)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---

@@

1. **Background: Return Migrants and Occupational Mobility in Sweden** 🌍➡️🇸🇪
    - Return migrants brought back financial capital, often invested locally, but didn't show much occupational upgrading on average.

2. **How are the individuals at the top of the skill distribution different from those who returned to farm?** 
    - Where did they move back to, how did their education change?

@@

::: {.column width="50%"}
![](assets/world_champtions.jpeg){fig-align="center" width=60%}
:::

@@

# Structuring biographies{background-color="#1C9E77"}

@@

timeline %>%
    filter(!is.na(start_year)) %>%
  arrange(start_year) %>%
  mutate(end_year_imputed = case_when(
    is.na(end_year) ~ lead(start_year),
    is.na(lead(start_year)) ~ start_year,
    TRUE ~ end_year
  )) %>%
  mutate(
    event = fct_reorder(event, start_year, .desc = TRUE)
  ) %>%
  # pivot_longer(c(start_year, end_year_imputed)) %>%
  # ggplot(aes(value, english_occupation, colour = name)) +
  ggplot(aes(xmin = start_year, xmax = end_year_imputed, y = event)) +
  geom_linerange(colour = "gray50", size = 2) +
  geom_point(aes(x = end_year_imputed), colour = "#be5d2b", size = 4) +
  geom_point(aes(x = start_year), colour = "#2B8CBE", size = 4) +
  labs(
    title = "Karl Lund's life course",
    subtitle = "Showing <span style = 'color:#2B8CBE;'>start dates</span> and <span style = 'color:#be5d2b;'>end dates</span> for his various roles and life events",
    x = NULL,
    y = NULL
  ) +
  theme(
    legend.position = "none",
    plot.subtitle = element_markdown(),
    plot.title.position = "plot",
    text = element_text(family = "ibm", size = 13)
  )

@@

<div style="text-align: center">

@@

</div>

Birthplaces of individuals who studied at Royal Tehcnical Institute (KTH) in *Who is Who in Industry and Business*

<div style="text-align: center">

```{r}
knitr::include_url("assets/kth_birthplace_map.html", height = "800")
```

</div>

# Classifying occupations{background-color="#1C9E77"}

@@

watchmaker_table %>% 
  tab_options(table.font.size = 40)
```

@@

occupation_table %>% 
  tab_options(table.font.size = 40)

@@

## Can we score how successful this is?

We can use a crosswalk from one schema to another as a test set, e.g. O * Net to ISCO:

![](assets/scoring_assignement.png){fig-align="center" width=100%}
